How P inanimate pronoun becomes R-pronoun-P On waarmee in Dutch

### 2020-01-12 paper.tex
einde zondag
niet veel gedaan.. maar er is een mooi overzicht in het schrift! schrijven nu
einde zondag
begonnen met prefix/suffix

This chapter is an in-depth study of the \tsc{r}-pronoun-postposition combination \tit{waarmee} `with what' in Dutch. This instance is interesting for two reasons. First, just like for all \tsc{r}-pronouns, the wh-element is the locative, but there is no meaning component related to location in `with what'. Second, the preposition \tit{met} `with' changes into \tit{mee} `with' when it is combined with an \tsc{r}-pronoun.

@@

In this section I investigate the internal structure of \tit{waarmee} `with what' and \tit{met wat} `with what' to capture the phonological similarities and differences between the two forms. First, I identify \tit{w} and \tit{a} as morphemes that appear in both expressions. Putting these two aside, I concentrate on \tit{ermee} `with it' and \tit{met 't} `with it'. I decompose these two expressions further, and end up arguing for a picture as shown in Table \ref{tbl:nofeatures}.
The elements \tit{w} and \tit{a} express the same syntactic structure in both expressions. The elements \tit{met} and \tit{'t} together also express the same features as \tit{mee} and \tit{er} together, but the distribution differs. \tit{Met} expresses less structure than \tit{mee}, and \tit{'t} expresses more structure than \tit{er}. \tit{Met} is shown to be an prefix, and \tit{mee} is a suffix. It also becomes clear that the \tit{er} in fact corresponds to the locative \tit{r} in Dutch.

@@

>>>>

This chapter is an in-depth study of the \tsc{r}-pronoun-postposition combination \tit{waarmee} `with what' in Dutch. This instance is interesting for two reasons. First, just like for all \tsc{r}-pronouns, the wh-element is the locative, but there is no meaning component related to location in `with what'. Second, the preposition \tit{met} `with' changes into \tit{mee} `with' when it is combined with an \tsc{r}-pronoun. To my knowledge, there is no account so far for this fact.

@@

In this section I investigate the internal structure of \tit{waarmee} `with what' and \tit{met wat} `with what' to capture the phonological similarities and differences between the two forms. First, I identify \tit{w} and \tit{a} as morphemes that appear in both expressions. Putting these two aside, I concentrate on \tit{ermee} `with it' and \tit{met 't} `with it'. I decompose these two expressions further, and end up arguing for a picture as shown in Table \ref{tbl:nofeatures}.

The elements \tit{w} and \tit{a} express the same syntactic structure in both expressions. The elements \tit{met} and \tit{'t} together also express the same features as \tit{mee} and \tit{er} together, but the distribution differs. \tit{Met} expresses less structure than \tit{mee}, and \tit{'t} expresses more structure than \tit{er}. \tit{Met} is shown to be an prefix, and \tit{mee} is a suffix. It also becomes clear that the \tit{er} in fact corresponds to the locative \tit{r} in Dutch.

@@

It differs per language and within a language how high a DP can move. Everything below is a suffix on the noun, everything higher is a preposition. Consider German full DP. Moves as high as above the dative, instrumental is expressed with a preposition.

\ex. mit ein loffel

but like i said, it also differs within a language, for example look at bulgarian here!

\ex.
\ag. Tazi duma m-i e nepoznata.\\
that word I-\tsc{dat} is unfamiliar\\
`That word is unfamiliar to me.'
\bg. Tazi duma e nepoznata sina mi.\\
that word is unfamiliar son my\\
`That word is unfamiliar my son.'
\bg. Tazi duma e nepoznata na sina mi.\\
that word is unfamiliar to son my\\
`That word is unfamiliar to my son.'
